`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-09 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
make code a bit more concise

```{r}
query_only_df <- library_has_cnv_df |>
  dplyr::filter(cell_group == "unknown") |>
  # create a finer cell type column for this plot
  dplyr::mutate(
    celltype_fine = ifelse(
      stringr::str_detect(ewing_annotation, "tumor"),
      "tumor",
      ewing_annotation
    )
  ) |>
  dplyr::add_count(celltype_fine) |>
  dplyr::mutate(
    celltype_fine_n = glue::glue("{celltype_fine} (n={n})"),
    # top 10 only
    celltype_fine_n = forcats::fct_lump(celltype_fine_n, 10)
  )

# add n() to "Other" for plot clarity and update factor to frequency order
current_levels <- levels(query_only_df$celltype_fine_n)
total_other <- query_only_df |>
  dplyr::filter(celltype_fine_n == "Other") |>
  nrow()
updated_other <- glue::glue("Other (n={total_other})")

query_only_df <- query_only_df |>
  dplyr::mutate(
    # update other level to have counts
    celltype_fine_n = as.character(celltype_fine_n),
    celltype_fine_n = ifelse(celltype_fine_n == "Other", updated_other, celltype_fine_n),
    # order based on freq
    celltype_fine_n = as.factor(celltype_fine_n),
    celltype_fine_n = forcats::fct_infreq(celltype_fine_n),
    celltype_fine_n = forcats::fct_relevel(celltype_fine_n, updated_other, after = Inf)
  ) |>
  # exclude small clusters
  dplyr::add_count(subcluster, name = "subcluster_size") |>
  dplyr::filter(subcluster_size >= 10)

# Create color palette with (n=) in labels
color_n_df <- query_only_df |>
  dplyr::select(celltype_fine, celltype_fine_n) |>
  dplyr::inner_join(
    colors_df,
    by = c("celltype_fine" = "celltype")
  ) |>
  dplyr::select(celltype_fine_n, color) |>
  unique()
colors <- color_n_df$color
names(colors) <- color_n_df$celltype_fine_n

# Add in the other color with its label, since that won't be in the palette
colors[updated_other] <- "#D2D2D2"
```

```{r, fig.width = 12}
ggplot(query_only_df) +
  aes(
    x = forcats::fct_infreq(subcluster),
    fill = celltype_fine_n
  ) +
  geom_bar() +
  scale_fill_manual(values = colors) +
  theme(axis.text.x = element_blank())
```

>>>>

```{r}
query_only_df <- library_has_cnv_df |>
  dplyr::filter(cell_group == "unknown") |>
  # create a finer cell type column for this plot
  dplyr::mutate(
    celltype_fine = ifelse(
      stringr::str_detect(ewing_annotation, "tumor"),
      "tumor",
      ewing_annotation
    ),
    # top 10 only - lump here to assist in color setup
    celltype_fine = forcats::fct_lump(celltype_fine, 10)
  ) |>
  dplyr::add_count(celltype_fine) |>
  dplyr::mutate(celltype_fine_n = glue::glue("{celltype_fine} (n={n})")) |>
  # exclude small clusters
  dplyr::add_count(subcluster, name = "subcluster_size") |>
  dplyr::filter(subcluster_size >= 10)

# Set cell type factor order by frequency, with the "Other (n=XX)" at the end
other_level <- grep("Other", unique(query_only_df$celltype_fine_n), value = TRUE)
query_only_df$celltype_fine_n <- forcats::fct_infreq(query_only_df$celltype_fine_n) |>
  forcats::fct_relevel(other_level, after = Inf)

# Create color palette with (n=) in labels
color_n_df <- query_only_df |>
  dplyr::select(celltype_fine, celltype_fine_n) |>
  dplyr::inner_join(
    colors_df,
    by = c("celltype_fine" = "celltype")
  ) |>
  dplyr::select(celltype_fine_n, color) |>
  unique()
colors <- color_n_df$color
names(colors) <- color_n_df$celltype_fine_n
```

```{r, fig.width = 12}
ggplot(query_only_df) +
  aes(
    x = forcats::fct_infreq(subcluster),
    fill = celltype_fine_n
  ) +
  geom_bar() +
  scale_fill_manual(values = colors) +
  labs(
    fill = "Cell type (number of cells)",
    x = "InferCNV subcluster"
  ) +
  theme(axis.text.x = element_blank())
```
